Evaluating the Supportive Effect of Feature Selection Methods on Machine Learning Models in Monitoring Forest Health Using Hyperspectral Remote Sensing Data

### 2020-04-05 docs/00-manuscripts/ieee/ieee-manuscript.tex
AB-review: Rephrase intro why FS is important, add pena ref

Despite its popularity in environmental modeling, there are no studies so far which used machine learning algorithms in combination with remote sensing data to analyze defoliation on a tree level.
This study aims to close this gap by analyzing defoliation at trees in northern Spain using airborne hyperspectral data.
We make use of the latest state-of-the-art methodology in machine learning by combining feature selection and hyperparameter tuning across multiple algorithms.
Incorporating the idea of creating data-driven \ac{NRI}s, this study also discusses the practical problems of high-dimensionality in environmental modeling \cite{trunk1979, xu2016}.

Even though \ac{ML} algorithms are capable of handling highly-correlated input variables, the fitting time of models increase substantially and the interpretation of results becomes more complicated.
At the same time, one has to deal with the presence of spatial autocorrelation in the data.
The dataset used in this study comes with a spatial grouping at the plot level which needs to be accounted for.

>>>>

Despite its popularity in environmental modeling, there are no studies so far which used machine learning algorithms in combination with remote sensing data to analyze defoliation on a tree level.
This study aims to close this gap by analyzing defoliation at trees in northern Spain using airborne hyperspectral data.
Method-wise it makes use of machine-learning methods in combination with feature selection and hyperparameter tuning.
Incorporating the idea of creating data-driven \ac{NRI}s, this study also discusses the practical problems of high-dimensionality in environmental modeling \cite{trunk1979, xu2016}.

Even though \ac{ML} algorithms are capable of handling highly-correlated input variables, model fitting becomes computationally more demanding, and model interpretation more complex.
At the same time, it is necessary to account for the presence of spatial autocorrelation in the data.
The dataset used in this study comes with a spatial grouping at the plot level which needs to be accounted for \cite{sperrorest, pena2015}.
